\documentclass{article}
\usepackage{a4wide}
\title{\emph{ Homework assignment 2 \\
      Questions 3,4 \& 6; Mind Strecthers 3        }}

\author{Daniel Ocampo}
\begin{document}
\maketitle 
\linespread{1.0}\selectfont
\textbf{ Study Questions 3,4,\& 6}
\begin{enumerate}
\item Define the seven major themes that charcterize the mind sets, attiudes, and actions of a successful entrepreneur. Which are are the most important and why?  How can they be encourged and why?

\begin{enumerate} 
	\item (Creative) most entrepreneurs are very good in finding clever ways to save money. 
	\item (obession) Having something that is always in the person mind.
	\item (courage ) the ability to do something even though you might have a setback 
	\item ( commitment and determination)  the ability to continue to do something.
	\item ( leadership) The ability to start something and share what is known to help improve. 
	\item ( motivation to excel) has relastic goals to move towards 
	\item (smart risk taker) know when to take risks, able to solve things that can be be dangerous
\end{enumerate}  


I think Creativity is the most important one because  it is kind of like strategy in the sense that you are doing something more than you competition. Not sure how it can be developed maybe take some art classes. 

\item Entrepreneurs are made, not born. Why is this so? Do you agree? 

according to the book it many years for someone develop a skill just intelligence alone is not enough. Well there is many factors to this I honestly don't know yet because this based on opnion and not factual information. On that note I would hope to say that entrepreneurs are made and not born. 

\item What is your personal entrepreneurial strategy?How should you change?

Don't have one yet but my guess is it shoud be diffrent from everyone else. it should change depending on the situation so it should be adaptible.

\end{enumerate}
\textbf{ Mind Stretcher 3}
\begin{enumerate}
\item How do you personlly stack up aginst the the seven entrereurial  mind set? What do you need to improve on?
I personlly do not have all of those traits, I am still working on myself, but I do Have courage in the sense that I am not afraid to take risks. I Do have commitment, and determination because even if I am bad at something there is no way I would give up on it until I finish. right now I lack motivation not sure what are my goals are right now but I know that I will find it soon and one way is by trying diffrent things. I have never been in a leadership postion but I would like to think that someday I will be once I have gained enough experince in a ceratian area.  Don't know if I am creative but with all the math classes I have taken I am sure to solve some problems not just in math but in real life. 

\end{enumerate}







\end{document}



